---
title: "p8105_hw1_xh2395"
author: "Xin  He"
date: "9/14/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##  problem 1

**Create a data frame as required:**
```{r problem1_df creat}
library(tidyverse)

problem1_df = tibble(
  vec_numeric = rnorm(8, mean = 0, sd = 1),
  vec_logical = vec_numeric > 0,
  vec_char = character(length = 8),
  vec_factor = factor(vec_char, levels = c("a", "b", "c"))
)
```


**Take the mean of each variable in the data frame:**
```{r mean}
mean(pull(problem1_df, vec_numeric))
mean(pull(problem1_df, vec_logical))
mean(pull(problem1_df, vec_char))
mean(pull(problem1_df, vec_factor))
```
The mean of vec_numeric and vec_logical works.
However, the mean of vec_char and vec_factor doesn't work.


**Convert variables from one type to another:**
```{r convert}
as.numeric(pull(problem1_df, vec_logical))
as.numeric(pull(problem1_df, vec_char))
as.numeric(pull(problem1_df, vec_factor))
```
After convert the logical, character, and factor variables to numeric variables, the logical variable shows as 0 or 1, the character variable shows as NA, the factor variable also shows as NA.
This helps explain why the  mean of vec_numeric and vec_logical works but the mean of vec_char and vec_factor doesn't work.


**Convert and multiply:**
```{r multiply}
as.numeric(pull(problem1_df, vec_logical))*pull(problem1_df, vec_numeric)
as.factor(pull(problem1_df, vec_logical))*pull(problem1_df, vec_numeric)
as.numeric(as.factor(pull(problem1_df, vec_logical)))*pull(problem1_df, vec_numeric)
```


## problem 2

**Create a data frame as required:**
```{r problem2_df creat}
problem2_df = tibble(
  x = rnorm(500, mean = 0, sd = 1),
  y = rnorm(500, mean = 0, sd = 1),
  vec_logical = x + y > 1,
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```
The size of the dataset is `r nrow(problem2_df)` and `r ncol(problem2_df)`.

The mean of x is `r mean(pull(problem2_df, x))`.

The median of x is`r median(pull(problem2_df, x))`.

The standard deviation of x is `r sd(pull(problem2_df, x))`.

The proportion of cases for which x + y > 1 is `r mean(pull(problem2_df, vec_logical))`.


**Make a scatterplot of y vs x (color points using the logical variable):**
```{r plot1}
ggplot(problem2_df, aes(x = x, y = y, color = vec_logical)) + geom_point()
```


**Export the first scatterplot to the project directory:**
```{r save}
ggsave("firstplot.png")
```


**Make a second scatterplot of y vs x (color points using the numeric variable):**
```{r plot2}
ggplot(problem2_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()
```


**Make a third scatterplot of y vs x (color points using the factor variable):**
```{r plot3}
ggplot(problem2_df, aes(x = x, y = y, color = vec_factor)) + geom_point()
```
